Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-04-11 paper_jasa.tex
modified definition of p-value

When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. Thus we define $p$-value for visual test $T_{\theta}$ as in definition \ref{dfn:pval}.
\begin{dfn} \label{dfn:pval}
The $p$-value of A visual test $T_{\theta}$ is at most $Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} (\frac{1}{m})^k(1-\frac 1m)^{(K-k)}}$ where $u$ is the observed number of successful evaluations.
\end{dfn}
% HH: I think this is covered by making power a property of the test
% In general,  $Pr(\text{Reject } H_0)$ is determined by the type of test being conducted.

>>>>

When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability $$Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} (\frac{1}{m})^k(1-\frac 1m)^{(K-k)}}$$ where $u$ is the observed number of successful evaluations. We use this probability to  define $p$-value for visual test $T_{\theta}$ as in definition \ref{dfn:pval}.
\begin{dfn} \label{dfn:pval}
The $p$-value associated with the decision of a visual test $T_{\theta}$ is given by 
    \begin{equation*}
        \begin{cases} 
              p-value \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
              p-value > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
        \end{cases}
    \end{equation*}
\end{dfn}
% HH: I think this is covered by making power a property of the test
% In general,  $Pr(\text{Reject } H_0)$ is determined by the type of test being conducted.
